### 2022-08-01 paper/akweury/document.tex
update eval

%% mean metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & & & & 9.82 \\ 
		\hline
		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & & & & 7.32\\ 
		\hline
		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & & & & 7.35 \\
		\hline
		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & & & & 9.15 \\
		\hline
		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & & & & 12.13\\
	\end{tabular}
	\caption{Average Angle Error of the evaluation dataset.}	
	\label{tab:eval-mean}
\end{table}

%% median metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & & & & 7.62 \\ 
		\hline
		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & & & & 4.01 \\ 
		\hline
		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & & & & 5.06 \\
		\hline
		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & & & & 5.81\\
		\hline
		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& & & & 6.76\\
	\end{tabular}
	\caption{Median Angle Error of the evaluation dataset.}	
	\label{tab:eval-median}
\end{table}

%% 5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l |l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & & & & 0.31\\ 
		\hline
		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & & & & 0.59 \\ 
		\hline
		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & & & & 0.50\\
		\hline
		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & & & & 0.45\\
		\hline
		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & & & & 0.41\\
	\end{tabular}
	\caption{Percent of error less than 5 degree of the evaluation dataset.}	
	\label{tab:eval-5d}
\end{table}

%% 11.5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 & & & & 0.69\\ 
		\hline
		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & & & & 0.83 \\ 
		\hline
		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & & & & 0.82\\
		\hline
		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 & & & & 0.75\\
		\hline
		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & & & & 0.66\\
	\end{tabular}
	\caption{Percent of error less than 11.5 degree of the evaluation dataset.}	
	\label{tab:eval-11d}
\end{table}

%% 22.5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & & & & 0.92\\ 
		\hline
		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & & & & 0.94\\ 
		\hline
		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & & & & 0.95\\
		\hline
		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & & & & 0.91\\
		\hline
		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & & & & 0.84\\
	\end{tabular}
	\caption{Percent of error less than 22.5 degree of the evaluation dataset.}	
	\label{tab:eval-22d}
\end{table}

%% 30 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & & & & 0.97 \\ 
		\hline
		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & & & & 0.96 \\ 
		\hline
		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & & & & 0.98 \\
		\hline
		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & & & & 0.95 \\
		\hline
		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & & & & 0.90\\
	\end{tabular}
	\caption{Percent of error less than 30 degree of the evaluation dataset.}	
	\label{tab:eval-30d}
\end{table}

@@

\newpage
\section{Surface Normal Inference based on Calibrated Illuminated RGBD images }

@@

@@

>>>>

%% mean metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 & & 9.82 \\ 
		\hline
		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & & 7.32\\ 
		\hline
		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & & 7.35 \\
		\hline
		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & & 9.15 \\
		\hline
		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & & 12.13\\
	\end{tabular}
	\caption{Average Angle Error of the evaluation dataset.}	
	\label{tab:eval-mean}
\end{table}

%% median metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & & 7.62 \\ 
		\hline
		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & & 4.01 \\ 
		\hline
		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & & 5.06 \\
		\hline
		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & & 5.81\\
		\hline
		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 & & 6.76\\
	\end{tabular}
	\caption{Median Angle Error of the evaluation dataset.}	
	\label{tab:eval-median}
\end{table}

%% 5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l |l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 & & 0.31\\ 
		\hline
		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & & 0.59 \\ 
		\hline
		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & & 0.50\\
		\hline
		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & & 0.45\\
		\hline
		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & & 0.41\\
	\end{tabular}
	\caption{Percent of error less than 5 degree of the evaluation dataset.}	
	\label{tab:eval-5d}
\end{table}

%% 11.5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 & & 0.69\\ 
		\hline
		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & & 0.83 \\ 
		\hline
		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & & 0.82\\
		\hline
		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & & 0.75\\
		\hline
		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & & 0.66\\
	\end{tabular}
	\caption{Percent of error less than 11.5 degree of the evaluation dataset.}	
	\label{tab:eval-11d}
\end{table}

%% 22.5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 & & 0.92\\ 
		\hline
		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & & 0.94\\ 
		\hline
		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & & 0.95\\
		\hline
		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 & & 0.91\\
		\hline
		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & & 0.84\\
	\end{tabular}
	\caption{Percent of error less than 22.5 degree of the evaluation dataset.}	
	\label{tab:eval-22d}
\end{table}

%% 30 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 & & 0.97 \\ 
		\hline
		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & 0.96 & & 0.96 \\ 
		\hline
		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & & 0.98 \\
		\hline
		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & & 0.95 \\
		\hline
		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & & 0.90\\
	\end{tabular}
	\caption{Percent of error less than 30 degree of the evaluation dataset.}	
	\label{tab:eval-30d}
\end{table}

@@

\newpage
\section{Visualized evaluation on Trip-Net models }

@@

%% F1-F4 eval

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f1.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f2.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_normal.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f4.png}
	\end{subfigure}

		\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f1.png}
		\caption{F1}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f2.png}
		\caption{F2}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_error.png}
		\caption{F3}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f4.png}
		\caption{F4}
	\end{subfigure}

	\caption{Comparison between different fusion times for Trip-Net. The first row is surface normal, the second row is the corresponding errors. The number in ``F$ x $" represents the fusion times. }
	\label{fig:tripnet-eval-synthetic-zoom-in}
\end{figure}

@@

\section{Trining on higher resolution}
We also prepared the dataset with resolution $ 512\times 512 $ for model evaluation. Higher resolution gives more information about the surface feature using the same model compare to lower resolution. The benefit is, if we extract a fixed sized patch from the normal map, say $ 32 \times 32 $, it might correspond a hindleg area of the dragon object in $ 128\times 128 $ resolution but maybe only a toe in $ 512\times 512 $ resolution. Therefore if we still use the same kernel size in the network for the same dataset, the higher the resolution it has, the less area it will cover. This is a good thing. Because then we only need to use these $ 32\times 32 $ points to calculate a toe in $ 512\times512 $ resolution image. But in $ 128\times128 $ resolution image, we use the same area $ 32\times32 $ to calculate the whole hindleg. In another word, we can also say that the higher resolution ``smooth" the object surface. Thus the higher resolution helps the model to calculate a more accurate normal map.

We use the same settings and the same models for training work on dataset with $ 512\times512 $ resolution. Figure \ref{fig:high_resolution_eval} gives a comparison among SVD, GCNN and Trip-Net models.
